New_Data_Coherence

### 2019-09-16 Analysis/Coherence_Calculations_New.Rmd
fix doubling up of diseases

Cat = bind_rows(dis_slopes_string_count %>% ungroup() %>% dplyr::select(Disease, Category) %>% distinct(), dis_slopes_biogrid_count %>% ungroup() %>% dplyr::select(Disease, Category) %>% distinct())

@@

coherence_disease =left_join(coherence_disease, Cat)

>>>>

Cat = bind_rows(dis_slopes_string_count %>% ungroup() %>% dplyr::select(Disease, Category), dis_slopes_biogrid_count %>% ungroup() %>% dplyr::select(Disease, Category) ) %>% distinct()

@@

coherence_disease =left_join(coherence_disease, Cat, "Disease")
